A Topic Model of Climate Change Literature

### 2019-06-13 methods.tex

	We use the references scraped from IPCC assessment reports from \citep{Minx2017l}, and attempt to match these with the results from the web of science. Table [x] shows the percentage of IPCC citations matched in each working group for each assessment report.

@@

	\subsection*{Non-negative Matrix Factorisation}

	Non-negative Matrix Factorisation (NMF) is an approach to topic modelling which factorises the term-frequency-inverse document frequency matrix \( V \) into the matrices \(W\), the topic-term matrix, and \( H \) the document-topic matrix, whose product approximates \(V\):

@@

	As demonstrated in Figure \ref{doc-topic}, each topic is represented as a set of word scores, and each document a set of topic scores. The combination of the two give the word scores in the document. For clarity in the figure, these are shown as simple counts, but in the model these are scaled according to each term's frequency within the corpus.

@@

	We calculate a topic's total score as the sum of document-topic scores. A topic's window score is the sum of document-topic scores considering only documents in the given time window. To represent a dynamic topic's newness, we multiply each assessment period number by the share of it's total score occurring in that window, and take the mean of these scores. A topic in which 100\% of documents which make it up occurred in assessment period 1 (6) would thereby receive a score of 1 (6), while a topic evenly distributed across all assessment periods would receive a score of 3.5.

%	\begin{figure}
%		\begin{center}
%			\includegraphics[width=1\linewidth]{plots/single_doc_3_536594.pdf}
%			\caption{SI Topic make up of a single document}
%			\label{doc-topic}
%		\end{center}
%	\end{figure}

>>>>

	We use the references scraped from IPCC assessment reports from \citep{Minx2017l}, and attempt to match these with the results from the web of science. Table \todo{}[x] shows the percentage of IPCC citations matched in each working group for each assessment report.

@@

	\subsection*{Topic Model}

	We use non-negative Matrix Factorisation (NMF), an approach to topic modelling which factorises the term-frequency-inverse document frequency matrix \( V \) into the matrices \(W\), the topic-term matrix, and \( H \) the document-topic matrix, whose product approximates \(V\):

@@

	As demonstrated in Figure \ref{doc-topic}, each topic is represented as a set of word scores, and each document a set of topic scores. The combination of the two give the word scores in the document. For clarity in the figure, these are shown as simple counts, but in the model these are scaled according to each term's frequency within the corpus as explained above.

	\subsubsection*{Model selection}

@@

	We calculate a topic's total score as the sum of document-topic scores. A topic's window score is the sum of document-topic scores considering only documents in the given time window. To represent a topic's newness, we multiply each assessment period number by the share of it's total score occurring in that window, and take the mean of these scores. A topic in which 100\% of documents which make it up occurred in assessment period 1 (6) would thereby receive a score of 1 (6), while a topic evenly distributed across all assessment periods would receive a score of 3.5.

	\subsubsection*{Disciplinary Entropy}

	\begin{figure}
		\begin{center}
			\includegraphics[width=1\linewidth]{plots_pub/topic_oecd_entropy.pdf}
			\caption{SI Disciplinary Entropy}
			\label{dis-entropy}
		\end{center}
	\end{figure}

	\begin{figure}
		\begin{center}
			\includegraphics[width=1\linewidth]{plots/single_doc_3_536594_1861.pdf}
			\caption{SI Topic make up of a single document}
			\label{doc-topic}
		\end{center}
	\end{figure}

	\begin{figure}
	\begin{center}
		\includegraphics[width=1\linewidth]{plots_pub/ipcc_rep_wcs_simplified.pdf}
		\caption{SI Representation by subfield}
		\label{subfield}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
		\includegraphics[width=1\linewidth]{plots_pub/wgs_socsci.pdf}
		\caption{SI Social science \& representation in topics across working groups}
		\label{socsci-wgs}
	\end{center}
\end{figure}
